%% CHEOPS 2026 Workshop @ EuroSys — 4-page paper
%% ACM sigplan format (2-column)
\documentclass[sigplan,nonacm,10pt]{acmart}

%% Remove ACM-specific metadata for workshop submission
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,backgrounds,calc,shapes.geometric}

%% Compact lists
\setlist{nosep,leftmargin=1.2em}

%% Shortcuts
\newcommand{\sysname}{\textsc{Ceph-SRE}\xspace}
\newcommand{\eg}{e.g.,\xspace}
\newcommand{\ie}{i.e.,\xspace}

\begin{document}

\title{\sysname: An Autonomous LLM Agent for On-Node\\Ceph Cluster Management}

\author{Vladislav Shabanov}
\affiliation{%
  \institution{University of California, Santa Cruz}
  \city{Santa Cruz}
  \state{California}
  \country{USA}
}
\email{vshabano@ucsc.edu}

% ─────────────────────────────────────────────────────────────────────
\begin{abstract}
Managing Ceph storage clusters remains largely manual: administrators
chain CLI commands, interpret JSON output, and follow ad-hoc runbooks
to diagnose failures.
We present \sysname, an autonomous agent that runs \emph{locally} on
commodity storage nodes and replaces brittle operator scripts with a
\emph{hybrid control loop}.
A \emph{Fast Path} handles routine queries (``list pools'', ``OSD
status'') through deterministic intent classification in a single
LLM call, while an \emph{Agent Path} activates a multi-step
\emph{ReAct} reasoning loop for complex diagnostics
(``fix degraded PGs'').
Both paths are protected by a four-tier safety framework that
classifies every action by risk level and gates destructive operations
on explicit confirmation.
We evaluate \sysname on an NVIDIA P100 node with five quantised
LLMs (3.8\,B--14\,B parameters) across 161 test cases spanning
intent classification, autonomous reasoning, safety enforcement,
and anomaly detection.
A 7\,B model achieves 85.5\% intent accuracy with 6\,s mean latency,
while safety classification and anomaly detection reach 100\%
accuracy regardless of model size---validating our design choice to
decouple deterministic safety logic from probabilistic LLM inference.
\end{abstract}

\maketitle

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================

Ceph~\cite{weil2006ceph} is the dominant open-source distributed
storage system, underpinning block, file, and object workloads in
production clouds.
Yet day-to-day operations---diagnosing degraded placement groups,
rebalancing OSDs after a disk replacement, predicting capacity
exhaustion---still depend on administrators manually invoking
\texttt{ceph osd tree}, \texttt{ceph pg dump}, and similar commands,
then mentally correlating the output.
Site-reliability teams encode this knowledge in shell scripts that
are brittle, cluster-specific, and difficult to maintain.

Recent advances in small language models (SLMs) make it feasible to
run 7--14\,B-parameter models on the same commodity hardware that
hosts Ceph OSDs.
This raises a compelling systems question: \emph{can an LLM-based
agent replace fragile operator scripts while running entirely on-node,
within the latency and safety envelope required for storage
management?}

We answer this with \sysname, a hybrid agent architecture whose key
contributions are:
\begin{itemize}
  \item A \textbf{dual-mode control loop} that routes simple CLI tasks
    to a deterministic fast path (single LLM call) and complex
    diagnostics to a multi-step ReAct~\cite{yao2023react} reasoning
    loop, achieving 100\% routing accuracy across all tested models.
  \item A \textbf{four-tier safety framework} that classifies 34
    Ceph operations into \textsc{low}/\textsc{medium}/\textsc{high}/\textsc{critical}
    risk levels, reaching 100\% risk classification accuracy
    independent of the underlying LLM.
  \item A \textbf{threshold-based anomaly detector} that scores
    cluster health across seven categories (health, OSD, PG,
    capacity, balance, performance, configuration) with perfect
    F1 on synthetic fault scenarios.
  \item An \textbf{empirical evaluation} on an NVIDIA P100 (12\,GB)
    comparing five local LLMs across 161 test cases, showing that
    a 7\,B quantised model is the practical sweet spot
    for on-node deployment.
\end{itemize}


% =====================================================================
\section{Design}\label{sec:design}
% =====================================================================

Figure~\ref{fig:arch} shows the overall architecture.
\sysname is structured as four cooperating subsystems:
a \emph{Hybrid Router} (\S\ref{ss:router}),
a \emph{ReAct Agent Loop} (\S\ref{ss:react}),
a \emph{Safety Framework} (\S\ref{ss:safety}), and
an \emph{Anomaly Detector} (\S\ref{ss:anomaly}).
All components share a \emph{Tool Registry} of 35 Ceph operations
and five pre-authored runbooks.

\begin{figure}[t]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[
  >=Stealth,
  node distance=0.6cm and 0.5cm,
  every node/.style={font=\small},
  box/.style={draw, rounded corners=2pt, minimum height=0.7cm,
              minimum width=2.0cm, align=center, fill=#1},
  box/.default={white},
  widebox/.style={draw, rounded corners=2pt, minimum height=0.7cm,
                  minimum width=4.4cm, align=center, fill=#1},
  widebox/.default={white},
  lbl/.style={font=\scriptsize\sffamily, text=black!60},
  arr/.style={->, thick},
  darr/.style={->, thick, dashed},
]

%% ── User input ──────────────────────────────────
\node[box=blue!8] (query) {User Query};

%% ── Router ──────────────────────────────────────
\node[widebox=orange!12, below=0.5cm of query] (router) {\textbf{Hybrid Router}\\[-1pt]{\scriptsize keyword check (24 triggers)}};

\draw[arr] (query) -- (router);

%% ── Two paths ───────────────────────────────────
\node[box=green!12, below left=0.7cm and 0.3cm of router] (fast) {\textbf{Fast Path}\\[-1pt]{\scriptsize 1 LLM call}};
\node[box=red!10, below right=0.7cm and 0.3cm of router] (react) {\textbf{Agent Path}\\[-1pt]{\scriptsize ReAct loop}};

\draw[arr] (router.south) -- ++(0,-0.2) -| node[lbl, above left, pos=0.25] {no keyword} (fast.north);
\draw[arr] (router.south) -- ++(0,-0.2) -| node[lbl, above right, pos=0.25] {keyword hit} (react.north);

%% ── Fast-path internals ─────────────────────────
\node[box=green!6, below=0.45cm of fast, minimum width=1.8cm] (intent) {Classify\\[-1pt]Intent};
\draw[arr] (fast) -- (intent);

%% ── ReAct internals ─────────────────────────────
\node[box=red!6, below=0.45cm of react, minimum width=1.8cm] (think) {Think};
\node[box=red!6, below=0.35cm of think, minimum width=1.8cm] (act) {Act};
\node[box=red!6, below=0.35cm of act, minimum width=1.8cm] (obs) {Observe};

\draw[arr] (react) -- (think);
\draw[arr] (think) -- (act);
\draw[arr] (act) -- (obs);
\draw[arr] (obs.east) -- ++(0.45,0) |- (think.east);
\node[lbl, right=0.5cm of act] {$\leq$10 steps};

%% ── Safety framework (spans both) ───────────────
\node[widebox=yellow!15, below=3.5cm of router] (safety) {\textbf{Safety Framework}\\[-1pt]{\scriptsize 4-tier risk: \textsc{low}\,/\,\textsc{med}\,/\,\textsc{high}\,/\,\textsc{crit}}};

\draw[arr] (intent.south) -- ++(0,-0.25) -| (safety.north west);
\draw[arr] (obs.south) -- ++(0,-0.15) -| (safety.north east);

%% ── Tool Registry ───────────────────────────────
\node[widebox=gray!10, below=0.45cm of safety] (tools) {\textbf{Tool Registry}\\[-1pt]{\scriptsize 35 tools \quad 5 runbooks}};

\draw[arr] (safety) -- node[lbl, right] {approved} (tools);

%% ── Ceph cluster ────────────────────────────────
\node[widebox=blue!8, below=0.45cm of tools] (ceph) {\textbf{Ceph RADOS Cluster}\\[-1pt]{\scriptsize OSD \,$\cdot$\, PG \,$\cdot$\, Pool \,$\cdot$\, MON}};

\draw[arr] (tools) -- (ceph);

%% ── Anomaly detector (side) ─────────────────────
\node[box=purple!10, left=0.6cm of tools, minimum width=1.6cm] (anomaly) {\textbf{Anomaly}\\\textbf{Detector}\\[-1pt]{\scriptsize 7 categories}};

\draw[darr] (ceph.west) -| (anomaly.south);
\draw[darr] (anomaly.north) |- (router.west);
\node[lbl, left=0.05cm of anomaly.north, anchor=south east] {alerts};

%% ── LLM (side) ──────────────────────────────────
\node[box=cyan!10, right=0.6cm of router, minimum width=1.4cm] (llm) {\textbf{Local}\\\textbf{LLM}\\[-1pt]{\scriptsize 7B Q4}};

\draw[<->, thick, dotted] (router.east) -- (llm.west);
\draw[<->, thick, dotted] (react.east) -| (llm.south);

\end{tikzpicture}%
}% end resizebox
\caption{\sysname architecture.  The Hybrid Router directs queries
to a single-call Fast Path or a multi-step ReAct Agent Path.
Both paths pass through the Safety Framework before reaching
the Tool Registry.  The Anomaly Detector monitors cluster
state independently and feeds alerts back to the router.
The local LLM (dashed) serves both intent classification and
autonomous reasoning.}
\label{fig:arch}
\end{figure}

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Hybrid Router}\label{ss:router}

On each user query, the router decides between two execution paths:

\smallskip\noindent
\textbf{Fast Path (Simple Mode).}\enspace
If the query contains none of 24 agent-trigger keywords
(\eg ``troubleshoot'', ``diagnose'', ``fix'', ``rebalance''),
the router issues a single LLM function-call to classify the
\emph{intent} and extract \emph{parameters}, then dispatches to the
corresponding tool.  This path completes in one LLM round-trip.

\smallskip\noindent
\textbf{Agent Path (ReAct Mode).}\enspace
Queries containing agent keywords are forwarded to the autonomous
reasoning loop (\S\ref{ss:react}).
The keyword check is a zero-cost string match that avoids an extra
LLM call for mode selection, contributing to the 100\% routing
accuracy we observe (\S\ref{sec:eval}).

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{ReAct Agent Loop}\label{ss:react}

Complex tasks are handled by a ReAct loop that iterates up to 10
steps (configurable) within a 120\,s session budget:

\begin{enumerate}
  \item \textbf{Think.}  The LLM receives the full tool schema, the
    current scratchpad of prior observations, and conversation
    context.  It emits a structured response containing a
    \emph{Thought}, an \emph{Action} (tool name), and
    \emph{Action Input} (parameters); or a \emph{Final Answer}
    if reasoning is complete.
  \item \textbf{Act.}  If the selected action is in the
    \emph{destructive set}
    (\texttt{delete\_pool}, \texttt{remove\_osd}, etc.),
    the safety framework (\S\ref{ss:safety}) must approve it before
    execution.  The tool's return value is recorded as an
    \emph{Observation}.
  \item \textbf{Loop.}  Steps repeat until a final answer is
    produced, the iteration limit is reached (in which case the
    scratchpad is summarised), or the time budget expires.
\end{enumerate}

The loop has access to 35 tools across seven categories: object
storage (11), cluster monitoring (8), cluster management (12),
documentation/RAG (2), configuration (2), runbook execution (3),
and planning (2).
Five pre-authored runbooks encode multi-step remediation procedures
(\eg \emph{Recover Down OSD}: health check $\to$ OSD status $\to$
PG impact $\to$ restart $\to$ verify).

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Safety Framework}\label{ss:safety}

Every action---whether initiated by the fast path or the agent
loop---passes through the \texttt{ActionEngine}, which enforces a
four-tier risk model over 34 mapped operations:

\begin{center}
\small
\begin{tabular}{@{}lrl@{}}
\toprule
\textbf{Risk Level} & \textbf{Actions} & \textbf{Policy} \\
\midrule
\textsc{low}      & 20 & Auto-approve (read-only) \\
\textsc{medium}   &  8 & Log, auto-approve \\
\textsc{high}     &  8 & Require confirmation \\
\textsc{critical} &  4 & Require confirmation + log \\
\bottomrule
\end{tabular}
\end{center}

An \texttt{ActionPolicy} object further constrains execution via
session-level rate limits (default 20 actions), dry-run mode,
and per-action allow/block lists.
Rollback templates exist for six reversible operations
(\eg \texttt{set\_osd\_out} $\leftrightarrow$ \texttt{set\_osd\_in}).
Crucially, risk classification is \emph{deterministic}---it is a
dictionary lookup, not an LLM inference---so its correctness is
independent of model quality.

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Anomaly Detector}\label{ss:anomaly}

The anomaly detector periodically scores cluster state across
seven categories using configurable thresholds
(\eg OSD utilisation warning at 75\%, critical at 85\%;
PG degraded $>$\,0 triggers a warning).
Each detected anomaly carries a severity
(\textsc{info}/\textsc{warning}/\textsc{critical}), and the
overall cluster score is computed as:
\[
  S = \max\!\Bigl(0,\; 100 - \!\!\sum_{\text{anomalies}}\!\! p_i\Bigr),
  \quad
  p_i = \begin{cases}
    25 & \text{critical} \\
    10 & \text{warning} \\
    2  & \text{info}
  \end{cases}
\]
Anomalies are linked to suggested runbooks for automated
remediation.  Like the safety framework, this component is
deterministic: it does not invoke the LLM.


% =====================================================================
\section{Evaluation}\label{sec:eval}
% =====================================================================

We evaluate \sysname across four axes: intent classification
accuracy (\S\ref{ss:intent}), ReAct reasoning quality
(\S\ref{ss:reacteval}), safety enforcement (\S\ref{ss:safetyeval}),
and anomaly detection (\S\ref{ss:anomalyeval}).
Latency is reported throughout.

\smallskip\noindent\textbf{Setup.}\enspace
All experiments run on a single CloudLab node with an
NVIDIA P100 GPU (12\,GB VRAM), representing commodity hardware
co-located with a Ceph OSD\@.
We serve models via Ollama and test five configurations:
\texttt{phi3.5} (3.8\,B, Q4),
\texttt{qwen2.5:7b} (Q4),
\texttt{llama3.1:8b} (Q4),
\texttt{qwen2.5:14b} (Q4), and
\texttt{llama3.1:8b-instruct-fp16}.
Embeddings use Sentence-Transformers \texttt{all-MiniLM-L6-v2}
(384-d) on CPU\@.
The test suite comprises 161 cases: 120~intent, 16~ReAct,
20~safety, and 5~anomaly scenarios.
Multi-run results (\texttt{qwen2.5:7b} and \texttt{llama3.1:8b})
report mean $\pm$ std over five independent runs.

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Intent Classification}\label{ss:intent}

Table~\ref{tab:intent} compares 120 natural-language queries across
12 intent categories (search, read, write, delete, statistics,
cluster monitoring, management, documentation, and edge cases).

\begin{table}[t]
\centering\small
\caption{Intent classification accuracy over 120 test queries.
Multi-run entries ($n{=}5$) show mean $\pm$ std.}
\label{tab:intent}
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Model} & \textbf{Params} & \textbf{Intent} & \textbf{Param} & \textbf{Latency} \\
& & \textbf{Acc.\,(\%)} & \textbf{Acc.\,(\%)} & \textbf{(ms)} \\
\midrule
phi3.5           & 3.8\,B & 55.8          & 72.5          & 6\,324 \\
llama3.1:8b      & 8\,B   & 82.5\,$\pm$\,0.8 & 91.0\,$\pm$\,0.4 & 10\,327 \\
\textbf{qwen2.5:7b} & \textbf{7\,B} & \textbf{85.5\,$\pm$\,0.8} & \textbf{89.2}  & \textbf{10\,542} \\
qwen2.5:14b      & 14\,B  & 85.0          & 88.3          & 13\,575 \\
llama3.1:8b-fp16 & 8\,B   & 80.8          & 90.0          & 28\,609 \\
\bottomrule
\end{tabular}
\end{table}

The 3.8\,B model falls below the usability threshold ($<$\,60\%),
confirming that storage-domain intent classification requires at
least a 7\,B model.
Scaling from 7\,B to 14\,B yields \emph{no accuracy gain}
(85.5\% vs.\ 85.0\%) while increasing latency by 29\%,
establishing diminishing returns for on-node deployment.
Perhaps counter-intuitively, the full-precision FP16 variant
(80.8\%) under-performs its Q4 counterpart (82.5\%), suggesting
that Ollama's Q4 quantisation preserves---or even regularises---the
instruction-following ability required for structured function calls,
while doubling inference time.

\smallskip\noindent
\textbf{Error analysis.}\enspace
The remaining ${\sim}$15\% errors concentrate in \emph{management
operations} (set\_osd\_out, create\_pool, etc.)\ that the LLM has
rarely seen during pre-training.
Documentation-versus-explanation confusion
(\texttt{search\_docs} $\leftrightarrow$ \texttt{explain\_issue})
accounts for another cluster of misclassifications, reflecting
inherent ambiguity in the queries.

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{ReAct Reasoning}\label{ss:reacteval}

We force each of 16 scenarios through both execution paths
and compare (Table~\ref{tab:react}).

\begin{table}[t]
\centering\small
\caption{ReAct vs.\ Simple mode on 16 diagnostic scenarios.
Tool coverage is the fraction of expected tools invoked.}
\label{tab:react}
\begin{tabular}{@{}lccccc@{}}
\toprule
\textbf{Model} & \textbf{Simple} & \textbf{ReAct} & \textbf{Tool} & \textbf{Avg} & \textbf{ReAct} \\
& \textbf{Succ.} & \textbf{Succ.} & \textbf{Covg.} & \textbf{Steps} & \textbf{Lat.\,(s)} \\
\midrule
phi3.5       &   0\%  & 100\% &  3\% & 1.0 & 18.7 \\
llama3.1:8b  & 81.2\% & 93.8\% & 71\% & 4.2 & 38.8 \\
\textbf{qwen2.5:7b}  & \textbf{75.0\%} & \textbf{93.8\%} & \textbf{58\%} & \textbf{4.5} & \textbf{35.1} \\
qwen2.5:14b  & 81.2\% & 100\% & 60\% & 2.4 & 48.6 \\
llama3.1:8b-fp16 & 81.2\% & 81.2\% & 67\% & 4.1 & 145.5 \\
\bottomrule
\end{tabular}
\end{table}

ReAct mode consistently outperforms simple mode on diagnostic tasks
(93.8--100\% vs.\ 0--81.2\%), validating the dual-path design.
The 14\,B model solves tasks in fewer steps (2.4 vs.\ 4.5) but at
higher wall-clock cost (48.6\,s vs.\ 35.1\,s).
Mode routing achieves \textbf{100\% accuracy} across all five
models, confirming that keyword-based switching is sufficient---no
learned classifier is needed.

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Safety \& Anomaly Detection}\label{ss:safetyeval}\label{ss:anomalyeval}

We test the action engine against 20 scenarios
(8~\textsc{low}, 6~\textsc{medium}, 3~\textsc{high},
3~\textsc{critical}) covering read-only queries, reversible
mutations, service-affecting operations, and cluster-wide flags.
Risk classification achieves \textbf{100\% accuracy} and confirmation
gating reaches \textbf{95\% accuracy} across \emph{all five models}.
This result is by construction: risk levels are determined by a
dictionary lookup, not by LLM inference.
The 5\% confirmation gap stems from a policy edge case where
\textsc{medium}-risk write operations are auto-approved under the default
policy threshold.

Five synthetic cluster states---from perfectly healthy to compound
failure (OSD down + near-full + degraded PGs)---are fed directly to
the anomaly detector.  All models yield identical results:
\textbf{100\% score accuracy} and \textbf{F1\,=\,1.0}
(macro-precision and recall both 1.000).
The detector correctly produces a score of 100 for the healthy
cluster, 0 for the compound failure, and intermediate scores
(30--65) for partial failures.
These scores are model-independent by design.

% - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Latency}\label{ss:latency}

Table~\ref{tab:latency} profiles end-to-end latency for 10
representative operations, each repeated 5 times.

\begin{table}[t]
\centering\small
\caption{Latency profile (ms) over 10 operations $\times$ 5
iterations.  CLI overhead is the ratio of agent to native \texttt{ceph} command latency.}
\label{tab:latency}
\begin{tabular}{@{}lrrrrc@{}}
\toprule
\textbf{Model} & \textbf{Mean} & \textbf{P50} & \textbf{P95} & \textbf{P99} & \textbf{CLI~$\times$} \\
\midrule
phi3.5        & 5\,041 & 4\,000 & 9\,012 & 17\,944 & 6.7$\times$ \\
\textbf{qwen2.5:7b}   & \textbf{6\,072} & \textbf{5\,759} & \textbf{8\,726} & \textbf{8\,819}  & \textbf{8.3$\times$} \\
llama3.1:8b   & 6\,295 & 6\,187 & 7\,567 & 7\,585  & 8.6$\times$ \\
qwen2.5:14b   & 8\,880 & 8\,893 & 10\,099 & 10\,145 & 12.6$\times$ \\
llama3.1:8b-fp16 & 14\,790 & 15\,057 & 17\,972 & 18\,279 & 21.7$\times$ \\
\bottomrule
\end{tabular}
\end{table}

The 7\,B Q4 models keep mean latency under 6.3\,s---an
8--9$\times$ overhead over raw CLI that is acceptable for
interactive operator sessions.
The 14\,B model exceeds the 10\,s interactive threshold at P95,
while FP16 inference is impractical at nearly 15\,s mean.
Latency is dominated by LLM inference;
RADOS round-trips contribute $<$\,700\,ms on average.

% =====================================================================
\section{Related Work}\label{sec:related}
% =====================================================================

\textbf{LLM agents for systems.}\enspace
Automated incident management has been explored in cloud
settings~\cite{chen2024automatic}, but these systems target
microservice architectures and rely on cloud-hosted LLMs (GPT-4).
\sysname runs entirely on-node with quantised open-weight models.
Concurrent work on LLM-based SRE assistants~\cite{ahmed2023recommending}
focuses on recommendation rather than autonomous execution.

\textbf{ReAct and tool-augmented LLMs.}\enspace
Yao et~al.~\cite{yao2023react} introduced the Thought-Action-Observation
loop; Schick et~al.~\cite{schick2023toolformer} demonstrated
self-taught tool use.
We adapt ReAct specifically for storage operations with a
domain-specific tool registry and safety interlock.

\textbf{AIOps for storage.}\enspace
Prior AIOps work focuses on anomaly detection in
telemetry~\cite{zhao2021empirical},
log analysis~\cite{he2021survey}, and
root-cause analysis~\cite{soldani2022anomaly}.
These approaches are complementary; \sysname integrates detection
with autonomous remediation via runbooks.

\textbf{Ceph management tooling.}\enspace
The Ceph Dashboard and \texttt{cephadm} provide GUI and
orchestration interfaces but lack natural-language interaction
or autonomous reasoning.
Rook~\cite{rook} automates Ceph lifecycle in Kubernetes but does
not address interactive diagnostics.


% =====================================================================
\section{Discussion}\label{sec:discussion}
% =====================================================================

\textbf{Model size sweet spot.}\enspace
Our results establish 7\,B Q4 as the minimum viable model size for
storage-domain agent tasks on a P100.
The negligible accuracy gain from 7\,B to 14\,B
(85.5\% $\to$ 85.0\%) suggests that domain-specific
prompt engineering and structured function-call schemas already
extract most of the available capability at 7\,B.
Future work will investigate whether fine-tuning on Ceph-specific
corpora can close the remaining 15\% accuracy gap.

\textbf{Deterministic safety by design.}\enspace
The 100\% safety and anomaly scores across all models are not
coincidental---they are architectural.
By implementing risk classification and threshold-based detection
as dictionary lookups and arithmetic rather than LLM
inference, we ensure that safety-critical components are
unaffected by model hallucinations or degradation.
This separation of concerns is essential for deploying LLM agents
in production storage environments.

\textbf{Latency--accuracy trade-off.}\enspace
The 8$\times$ CLI overhead is dominated by LLM inference and is
acceptable for interactive management sessions (operators rarely
need sub-second cluster diagnostics).
For latency-sensitive monitoring, the anomaly detector runs
independently of the LLM in $<$\,1\,ms.

\textbf{Limitations.}\enspace
Our evaluation uses synthetic anomaly scenarios rather than live
fault injection; a production deployment would benefit from
chaos-engineering-style testing.
The 120-query intent suite, while comprehensive, does not yet cover
multi-tenant or RBAC-aware scenarios.
The keyword-based router, though 100\% accurate on our test set,
may misroute novel phrasings in production.


% =====================================================================
\section{Conclusion}\label{sec:conclusion}
% =====================================================================

We presented \sysname, a hybrid LLM agent for autonomous Ceph
cluster management that runs on commodity GPU hardware.
Our evaluation across five models and 161 test cases shows that:
(1)~a 7\,B quantised model is sufficient for 85.5\% intent accuracy
at 6\,s latency;
(2)~deterministic safety and anomaly components achieve 100\%
accuracy regardless of model quality; and
(3)~the dual-mode control loop achieves 100\% routing accuracy
with zero-cost keyword matching.
These results demonstrate that on-node LLM agents are a practical
replacement for manual operator scripts in storage cluster management.


% =====================================================================
\balance
\bibliographystyle{ACM-Reference-Format}

\begin{thebibliography}{10}

\bibitem{weil2006ceph}
S.~A. Weil, S.~A. Brandt, E.~L. Miller, D.~D.~E. Long, and C.~Maltzahn.
\newblock Ceph: A scalable, high-performance distributed file system.
\newblock In \emph{Proc.\ OSDI}, 2006.

\bibitem{yao2023react}
S.~Yao, J.~Zhao, D.~Yu, N.~Du, I.~Shafran, K.~Narasimhan, and Y.~Cao.
\newblock {ReAct}: Synergizing reasoning and acting in language models.
\newblock In \emph{Proc.\ ICLR}, 2023.

\bibitem{schick2023toolformer}
T.~Schick, J.~Dwivedi-Yu, R.~Dess\`{i}, R.~Raileanu, M.~Lomeli,
  L.~Zettlemoyer, N.~Cancedda, and T.~Scialom.
\newblock {Toolformer}: Language models can teach themselves to use tools.
\newblock In \emph{Proc.\ NeurIPS}, 2023.

\bibitem{chen2024automatic}
X.~Chen, et~al.
\newblock Automatic root cause analysis via large language models for cloud
  incidents.
\newblock In \emph{Proc.\ EuroSys}, 2024.

\bibitem{ahmed2023recommending}
T.~Ahmed, et~al.
\newblock Recommending root-cause and mitigation steps for cloud incidents
  using large language models.
\newblock In \emph{Proc.\ ICSE}, 2023.

\bibitem{zhao2021empirical}
N.~Zhao, et~al.
\newblock An empirical investigation of practical log anomaly detection for
  online service systems.
\newblock In \emph{Proc.\ ESEC/FSE}, 2021.

\bibitem{he2021survey}
S.~He, J.~Zhu, P.~He, and M.~R. Lyu.
\newblock A survey on automated log analysis for reliability engineering.
\newblock \emph{ACM Computing Surveys}, 54(6), 2021.

\bibitem{soldani2022anomaly}
J.~Soldani and A.~Brogi.
\newblock Anomaly detection and failure root cause analysis in (micro)service
  systems: A survey.
\newblock \emph{ACM Computing Surveys}, 55(3), 2022.

\bibitem{rook}
Rook Authors.
\newblock Rook: Open-source, cloud-native storage for {Kubernetes}.
\newblock \url{https://rook.io/}, 2024.

\end{thebibliography}

\end{document}
